Collaborator Agreement

### 2021-12-05 docs/collaborator_agreement/collaborator_agreement.Rmd
♻️ - editcollab agreement

This agreement provides guidelines for the paper: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses" accepted as a [Registered Report](https://www.cos.io/initiatives/registered-reports) at Advances in Methods and Practices in Psychological Science ([AMPPS](https://www.psychologicalscience.org/publications/ampps).)

@@

- Analyse (as an individual or in a team) the dataset to answer the research question as you see fit.
- Submit your analysis report (as an individual or in a team), in the form of "Methods" and "Results" sections, and fill in a data analysis questionnaire by 2022-04-14, 23.59 UTC.
- Review (as an individual or in a team) four analyses reports and submit the review report by 2022-05-31, 23.59 UTC)
- Read and approve the final manuscript (due 2022-08-31, 23.59 UTC)

@@

Principal Investigators (PIs) of contributing labs are responsible for their students and staff working on the project. This includes: honestly reporting the contributions of their lab members, evaluating whether contributions merit authorship according to the above statement and the CRediT table, and verifying that contributions are correctly described in any formal publication.

@@

*Section 1 (project coordinators)*. The project coordinators (Stefano Coretta, Joseph Casillas, and Timo Roettger) will occupy first and second author positions, respectively (Stefano Coretta and Joseph Casillas) and the last author positions (Timo Roettger). These three authors will be listed: Coretta, Casillas, ..., Roettger-

@@

*Section 2 (design of study materials and data collection)*. Two additional authors that were involved in study design and data collection (Simon Roessig, Michael Franke), will occupy position 3 and 4 in the author list.

*Section 3 (analysts)*. Position from 5 on will be occupied by all analysts involved in alphabetical order.

@@

Each contributor is personally accountable for the accuracy and integrity of their work on this project. This includes ensuring that (1) you are operating in accordance with your local research rules and regulations, (2) your specific research products are honest and accurate (e.g., data, translations, code), and (3) your description of your role on the project is accurate.

@@

Initial press releases will be coordinated by the Project coordinators. All collaborators are strongly encouraged to speak to the press, but are expected to (1) emphasize the highly collaborative nature of the research project and (2) encourage the interviewer to reach out to various members of the team.

>>>>

This agreement provides guidelines for the paper: *Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses* accepted as a [Registered Report](https://www.cos.io/initiatives/registered-reports) at Advances in Methods and Practices in Psychological Science ([AMPPS](https://www.psychologicalscience.org/publications/ampps).)

@@

- Analyse (as an individual or in a team) the dataset to answer the research question as you see fit.
- Submit your analysis report (as an individual or in a team), in the form of "Methods" and "Results" sections, and fill in a data analysis questionnaire by 2022-04-15, 23.59 UTC.
- Review (as an individual or in a team) four analyses reports and submit the review report by 2022-05-31, 23.59 UTC)
- Read and approve the final manuscript (due 2022-08-31, 23.59 UTC)

@@

The Team Coordinators (TCs) of contributing teams are responsible for their students and staff working on the project. This includes: honestly reporting the contributions of their lab members, evaluating whether contributions merit authorship according to the above statement and the CRediT table, and verifying that contributions are correctly described in any formal publication.

@@

**Section 1** Pproject Coordinators). The Project Coordinators (Stefano Coretta, Joseph Casillas, and Timo Roettger) will occupy first and second author positions, respectively (Stefano Coretta and Joseph Casillas) and the last author positions (Timo Roettger). These three authors will be listed: Coretta, Casillas, ..., Roettger-

@@

**Section 2** (design of study materials and data collection). Two additional authors that were involved in study design and data collection (Simon Roessig, Michael Franke), will occupy position 3 and 4 in the author list.

**Section 3** (analysts). Position from 5 on will be occupied by all analysts involved in alphabetical order.

@@

Each contributor is personally accountable for the accuracy and integrity of their work on this project. This includes ensuring that:

1. You are operating in accordance with your local research rules and regulations.
2. Your specific research products are honest and accurate (e.g., data, translations, code).
3. Your description of your role on the project is accurate.

@@

Initial press releases will be coordinated by the Project coordinators. All collaborators are strongly encouraged to speak to the press, but are expected to:

1. Emphasize the highly collaborative nature of the research project.
2. Encourage the interviewer to reach out to various members of the team.
